\section{Design}
The design goal of MichelinCook is to provide timing based delivery of flash cards containing cooking directions. Following are the important design goals of the application.

\begin{enumerate}
	\item Easy search and access to Recipes
	\item Access to latest trending recipes and curated recipes from popular chefs
	\item Finding recipes based on categories like 'Cuisines, 'Quick \& Easy', 'Cheap Eats' and 'Healthy'
	\item Direct search for a recipe from every page
	\item Easy navigation throughout the app
	
\end{enumerate}

\begin{itemize}
\item Interactive content delivery for cooking
\item Table of required quantity of ingredients for selected recipe
\item The quantity of ingredients are appropriately changed depending on the number of servings selected
\item Cook-top size is considered to scale the time required for each cooking step
\item Timer enabled flash cards containing cooking direction and picture to assist while cooking
\item Ability to navigate to any step of the cooking procedure
\end{itemize}

The above listed features will help provide user with an easy and direct way to cook from. The overall experience is further enhanced by a simple UI design.

\section{Social and Cognitive Issues}
It should go without saying that smartphones make our lives easier in many ways. They help us find directions to our next destination, maintain communication with loved ones and dear friends, and even waste precious time playing games. We carry our phones with us everywhere we go, be it our living room, work space, or even the bathroom. So why shouldn't we venture with it into the kitchen? Cooking apps are the next step in the complete mobile takeover.

The app revolution is leaving no sphere of life untouched, not even the kitchen. With more devices featuring large and vivid touch screens, it is trivial to realize that a good tablet with the right apps can make for a handy digital cookbook, able to help home cooks and pro chefs discover and organize recipes, track shopping lists and organize menus and meal calendars. From recipe discovery apps and classic cookbooks, to personal recipe organizers, there are now apps for Android, iOS, Windows Phone and Windows 8 devices.

But with MichelinCook user experiences features that are clear and concise. The digital cards provides a unique solution to enable users to cook a variety of dishes. The digital cards are designed for ease of learning, with step-by-step instructions, allowing users to see exactly what's going on all the time.