\begin{thebibliography}{50}

\bibitem{CardView} CardView | Android Developers  [Online] May 2015. Available: https://developer.android.com/reference/\\android/support/v7/widget/CardView.html

\bibitem{lollipop} Android - 5.0 Lollipop [Online] May 2015. Available: https://www.android.com/intl/\\en\_us/versions/lollipop-5-0/

\bibitem {fragments} Fragments | Android Developers  [Online] May 2015. Available: http://developer.android.com/guide/components\\/fragments.html

\bibitem {activites} Activites | Android Developers  [Online] May 2015. Available: http://developer.android.com/guide/components\\/activities.html

\bibitem{LeanStartup} The Lean Startup | Methodology [Online] May 2015. Available: http://theleanstartup.com/principles

\bibitem{MVP} The Lean Startup | Methodology [Online] May 2015. Available:
http://theleanstartup.com/principles

\bibitem{cook-top} D. Ding, R. A. Cooper, P. F. Pasquina, and L. Fici-Pasquina, ''Sensor technology for smart homes,'' Maturitas, vol. 69, no. 2, pp. 131 - 136, 2011.

\bibitem{cook-top1} S.R. Patil, Raveena Chavan, ''Intelligent Cooking Providing Automatic Time and Temperature Setting Using Image Processing With Wide Range of Recipes for Microwave Ovens'', Department of Computer Engineering, Pune University, Pune, India. received on December, 2013.

% \bibitem{MichelinCook} Murcott,A.(1983) ''Women's Place: CookBook's images of technique and technology in the British Kitchen'',Women's Studies International forum,Vol.6,No.1,pp.33-9.

\end{thebibliography}